Small(er) Samples

### 2021-10-12 R/smaller_samples.Rmd
remove samples with no mass.

df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)
df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521")
```

```{r}
df %>% 
ggplot(aes(mass, c12ua, color = as.factor(rec_num))) +
  geom_point()
```

>>>>

df <- read_csv(here("data_analysed/carb_all_results.csv")) %>% 
  compare_consensus() %>% 
  mutate(c12ua = he12C * 1E6)
samples <- read_csv(here("data/carb_data.csv")) %>% 
  select(wheel, pos, mass, he_added)
df <- left_join(df, samples, by = c("wheel", "pos")) %>% 
  filter(wheel != "USAMS020521",
         !is.na(mass))
```

### Size and Current

Until we get below 10mg of carbonate, any size-current relationship is mostly obscured by other factors.

```{r}
df %>% 
ggplot(aes(mass, c12ua, color = Name)) +
  geom_point() +
  ggtitle()
```
